Atomify - a live LAMMPS visualizer

### 2017-06-16 ms.tex
Reordering figures

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{flowchart.png}
	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications. a) A LAMMPS script is written using a text editor. b) Simulation is performed from the terminal. c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}. Atomify simplifies the workflow by combining all steps into a single application. }
	\label{fig:flowchart}
\end{figure}

@@

A simplified version of Atomify is made available for mobile platforms (Android
and iOS).
This version of Atomify provides access to some of the examples and is intended
for exploration of molecular dynamics simulations by students.
It also works as a demonstration of the visualization capabilities of the
desktop version of the software.
The authors are optimistic that teachers can use the visualizations provided by
Atomify to explain microscopic interactions underlying concepts in topics such
as thermodynamics, geophysics, and biology.
\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{gui.png}
	\caption{%
    Overview of the Graphical User Interface (GUI) in Atomify.
    The toolbar (1) provides changing
    between editing, viewing and analyzing the running simulation,
    in addition to playback controls.
    The file browser (2) contain the list of open LAMMPS scripts or data files.
    The text editor (3) provides code highlighting.
    The viewport (4) shows the current simulation.
    The simulation properties (5) shows the simulations details, gives access to 
    LAMMPS objects such as groups, regions and computes, and the rendering
    properties (6) lets you change the viewport settings, such as lighting and
    draw mode.
    TODO: Add numbers to figure.
    }
	\label{fig:gui}
\end{figure*}
\section{Features}

@@

Performance improvements are planned by for instance using geometry shaders to
generate periodic copies.
Currently this is partially done on the CPU,
which  reduces performance drastically.
We also aim to include more backends, both using the CPU and GPU,
in addition to running simulations on computing clusters while visualizing them
on the users own computer.

>>>>

@@

A simplified version of Atomify is made available for mobile platforms (Android
and iOS).
This version of Atomify provides access to some of the examples and is intended
for exploration of molecular dynamics simulations by students.
It also works as a demonstration of the visualization capabilities of the
desktop version of the software.
The authors are optimistic that teachers can use the visualizations provided by
Atomify to explain microscopic interactions underlying concepts in topics such
as thermodynamics, geophysics, and biology.
\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{gui.png}
	\caption{%
    Overview of the Graphical User Interface (GUI) in Atomify.
    The toolbar (1) is used to change between the different modes, such as 
    editing, viewing and analyzing the running simulation, 
    in addition to playback controls.
    The file browser (2) contain the list of open LAMMPS scripts or data files.
    The text editor (3) provides code highlighting.
    The viewport (4) shows the current simulation.
    The simulation properties (5) shows the simulations details, gives access to 
    LAMMPS objects such as groups, regions and computes, and the rendering
    properties (6) lets you change the viewport settings, such as lighting and
    draw mode.
    TODO: Add numbers to figure.
    }
	\label{fig:gui}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{flowchart.png}
	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications. a) A LAMMPS script is written using a text editor. b) Simulation is performed from the terminal. c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}. Atomify simplifies the workflow by combining all steps into a single application. }
	\label{fig:flowchart}
\end{figure*}

\section{Features}

@@

Performance improvements are planned by for instance using geometry shaders in
the rendering pipeline.
This allows a fourfold reduction in the number of vertices passed from the CPU
to the GPU.
Further, geometry shaders can be used for certain modifiers,
such as the periodic copies, which are currently performed on the CPU.

% TODO Reference to KOKKOS
We also aim to include more LAMMPS backends, such as KOKKOS, and running
simulations on computing clusters while visualizing them on the users own
computer.
